---
title: "An example RMarkdown file"
author: "Timo Grossenbacher, SRF Data"
date: "04/09/2015"
output: html_document
---

This is an example R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

Inside this document, you show your audience what you did in your analysis. You can also include a link to the downloadable RScript, [like so](http://grssnbchr.github.io/rddj-reproducibility-workflow/rscript.zip).

You can also include code from other scripts:

```{r}
source("processData.R")
```

Example script that takes something from input and writes a png to output
```{r}
# read csv from input
data <- read.csv("input//data.csv")
# transform it using a sourced function
processedData <- doSomething(data)

# generate an output folder if it doesn't exist
dir.create(file.path(getwd(), 'output'), showWarnings = F)
# plot
png(filename = "output/image.png")
plot(processedData)
dev.off()
plot(processedData)
```